Towards Contract Modules for the Tezos Blockchain

### 2021-05-26 papers/contract-modules/fmbc2021/fmbc-main.tex
+bartoletti

The basic idea of our advanced checking, namely precondition checking, is derived from the Java modeling language (JML)\cite{Leavens2006DesignBC, 101007}, in which the behavior of program components is described as an executable contract between Java program and its clients. This executable contract specifies preconditions that must be satisfied by clients and postconditions that are guaranteed by the program. A precondition supplied with a client call must be verified  before a function defined by the program is called, and the program guarantees that the postconditions are satisfied in return after the call. The original use of such preconditions and postconditions dades back to Hoare's paper on formal verification \cite{101145}. The executable contracts are written as program code in the programming language. In our approach, the safe contract module in the Ocaml language plays a role as an executable contract. Several applications are based on JML \cite{Tran2017, keY}. Ahrendt et al. \cite{keY} propose a framework called The KeY for deductive software verification.

>>>>

The basic idea of our advanced checking, namely precondition checking,
is inspired by JML, the Java modeling
language~\cite{Leavens2006DesignBC, 101007}, in which the behavior of 
program components is described as a contract between Java
program and its clients. This contract specifies
preconditions that must be satisfied by clients and postconditions
that are guaranteed by the program. A precondition supplied with a
client call must be verified before a function defined by the program
is called, and the program guarantees that the postconditions are
satisfied in return after the call. The original idea of using
preconditions and postconditions dates back to Hoare's paper
\cite{101145}. Software contracts have also been proposed for
blockchain \cite{DBLP:journals/fbloc/Bartoletti20}.
% The executable contracts are written as program code in
% the programming language.
In our approach, the safe contract module in the Ocaml language comes
close to contracts in this sense. Several
applications are based on JML \cite{Tran2017}. Ahrendt et
al. \cite{keY} propose the KeY framework for deductive software
verification.
